Exploratory data analysis

### 2020-02-15 analysis/eda.Rmd
wflow_publish(knitr_in("analysis/eda.Rmd"), view = FALSE, verbose = TRUE)

```{r}
compare_buffer <- function(trees_with_buffer, trees_without_buffer, plot_name) {
  if (plot_name == "laukiz1") {
    targets_sub_ids <- 1
  } else if (plot_name == "laukiz2") {
    targets_sub_ids <- 2
  } else if (plot_name == "luiando") {
    targets_sub_ids <- 3
  } else if (plot_name == "oiartzun") {
    targets_sub_ids <- 4
  }

>>>>

```{r buffer-size-comp}
compare_buffer <- function(trees_with_buffer, trees_without_buffer, plot_name) {
  if (plot_name == "laukiz1") {
    targets_sub_ids <- 1
  } else if (plot_name == "laukiz2") {
    targets_sub_ids <- 2
  } else if (plot_name == "luiando") {
    targets_sub_ids <- 3
  } else if (plot_name == "oiartzun") {
    targets_sub_ids <- 4
  }
